\begin{acknowledgements}


    This dissertation would not have been possible
    without the support of many mentors, colleagues, friends and family.
    To my advisor, Professor Kam-Biu Luk,
    thank you for guiding me through my growth as a researcher these past seven years.
    Your curiosity is contagious:
    even before I officially joined your research group,
    you pitched me on all sorts of side projects
    like the laser electron accelerator
    and water-based liquid scintillator.
    I appreciate that you supported my detour into the LArPix project,
    where I was able to develop valuable hardware and electronics experience.
    When I faced setbacks, you reminded me that
    a main goal of being a researcher is to have fun.

    To my colleagues in the LBNL Neutrino Group over the years,
    Herb, Dan, Cheng-Ju, Brooke, Chris, Yasu, Patrick, Matt, Henoch and Peter:
    I could not have asked for better research collaborators / lunch companions.
    Breaking bread with you every day was one of the first things I started missing
    at the start of the pandemic.
    Herb, thank you for raising all the questions I could not answer
    and pointing out all the problems with my data that I tried to paper over;
    your zeal for clear answers has made me a better scientist.
    Dan, thank you for your mentorship and leadership on the LArPix project,
    and for helping me to nail down my plans for this dissertation
    at both the beginning and the end of the journey.

    I must thank my undergraduate research advisors,
    Professors Szabolcs Marka and Brian Cole.
    You taught me the foundations for being a successful particle physicist:
    clear and detailed talks, and lots of plots.
    And to my high-school physics teacher, Mr.~Vaughan,
    thank you for making physics seem hard yet doable,
    mysterious yet intuitive.
    Some of your lessons --- particularly ``Step 1: draw a free-body diagram''---
    inform how I approach difficult problems to this day.
    I apologize for including semicolons in this dissertation.

    I would long ago have given up hope of completing this dissertation
    were it not for the support and camaraderie of my friends in Berkeley.
    Neil, Chelsea, Alex, Steve, Kyle, Amy, Matt, Claire, both Chrises, Crystal,
    and Justin:
    from Tuolomne Meadows and Death Valley to Golden Gate Fields and Jupiter,
    we all proved that it really is possible to be a grad student
    and a balanced human being at the same time.
    Thank you all for being there for me, both for the pep talks
    and the celebrations.
    To Simca, thank you for your trust in me as we built
    Respect is Part of Research together to make our department
    a safer place to work.

    My union, UAW Local 2865, gave me opportunities to learn and to lead.
    Thank you to Vetri for bringing me to my first union meeting, and
    to David for having the audacity to invite me to a 2-day organizing training
    just 15 minutes after we first met.
    Garrett, Kavitha, Zach, Greg and Gwen, you all were the reason
    I looked forward to the day-to-day experience of union organizing.

    Mom and Dad, you have supported me literally from Day One.
    You fostered in me a love of learning, a love of music,
    and a love of community.
    Most importantly, you held it together for eight years
    while I worked towards my degree 3000 miles away.
    Thank you for asking whether I'm moving back only once every few phone calls.
    Tom, thank you for shouldering the burden of being the only Kohn brother
    at family gatherings when I wasn't able to fly home.

    To my wife, Jaime, thank you for believing in me,
    for letting me air my frustrations when my code wasn't working,
    for helping me plan my writing schedule,
    for doing \SI{90}{\percent} of the housework while I was
    locked in the office writing,
    for bringing me thesis fuel snacks,
    for planning excursions on my days off,
    for planning meals on my writing days,
    for putting things in perspective when plans went awry,
    for advocating for me to myself when I was too stressed to think straight,
    for learning about my research,
    and for agreeing that we should spend the rest of our lives together.




\end{acknowledgements}
